Improving the modelling of tempo and phoneme duration

### 2017-04-06 Paper/Paper_v1.tex
a table
Another table

As the results of the initial two models were encouraging, we proceeded with a ``real`` model. For this, we reconstructed to a great extent a previous experiment \cite{Brinckman2003} that used a CART tree to predict phoneme duration, and reached good approximation values. By using this model we also had the advantage of having a reference for comparison. There is only one feature out of the 19 used in that experiment, which we could not recreate: degree of word accentuation. We lacked prosodic information for doing this. However, we tried to capture this kind of information by adding two extra word type classes: emphatic function words, like interjections and answer particles, and emphatic content words, like proper names and spelled items. For such words it is generally known that they usually carry phrasal stress.

@@

\section{Results}
We trained and evaluated both a M5P and a REPTree model. The results were very similar, so present here only the results obtained using the model tree M5P, as they were slightly better. As can be seen in Table ... adding the speech rate feature caused a significant improvement of all our models.

Table

However, the performance of our model tree is smaller than the performance of the CART built by Brinckmann \& Trouvain \cite{Brinckman2003}. This is explainable if we consider the nature of the used datasets. The CART tree used PhonDat, a rather homogenous dataset in terms of speech rate and number of speakers. Furthermore, the model was trained and tested separately on data produced by one speaker. The reported results show even for PhonDat a difference in performance between speakers. Another aspect that can have a great impact on the model result is the quality of the input data. While PhonDat was manually segmented and annotated, Verbmobil was processed automatically using the MAUS segmentation system. When evaluating outliers we found many examples of wrong segmentation, as we also discussed in Section 4.2.

@@

>>>>

As the results of the initial two models were encouraging, we proceeded with a ``real`` model. For this, we reconstructed to a great extent a previous experiment \cite{Brinckmann_2003} that used a CART tree to predict phoneme duration, and reached good approximation values. By using this model we also had the advantage of having a reference for comparison. There is only one feature out of the 19 used in that experiment, which we could not recreate: degree of word accentuation. We lacked prosodic information for doing this. However, we tried to capture this kind of information by adding two extra word type classes: emphatic function words, like interjections and answer particles, and emphatic content words, like proper names and spelled items. For such words it is generally known that they usually carry phrasal stress.

@@

\section{Results}
We trained and evaluated both a M5P and a REPTree model. The results were very similar, so present here only the results obtained using the model tree M5P, as they were slightly better. As can be seen in Table \ref{tab:perfM} adding the speech rate feature caused a significant improvement on all our models.

\begin{table}[htbp]
\centering
%\vspace{10mm}
\begin{tabular}{|l|c|c|c|c|c|}

\hline
	 & Basic - SR & Basic + SR & M5P - SR & M5P + SR & CART\\
\hline
\hline
Correlation coef 		& .42  &  & .50 & .79 & .86 / .83\\
	\hline
MAE  &  31.02 & & 34.21 & 25.19 & 22.46 / 21.40\\
	\hline
RMSE  &  47.09 & & 62.91 & 44.70 & NA \\
	\hline

\end{tabular}
\caption{Overview of the performance results of 3 models with (+) and without (-) speech rate (SR). CART is the model created by Brinckmann \& Trouvain \cite{Brinckmann_2003}. The two values in the CART cells represent the performance obtained for 2 different speakers.} 
\label{tab:perfM}
\end{table}

However, the performance of our model tree is smaller than the performance of the CART built by Brinckmann \& Trouvain \cite{Brinckmann_2003}. This is explainable if we consider the nature of the used datasets. The CART tree used PhonDat, a rather homogenous dataset in terms of speech rate and number of speakers. Furthermore, the model was trained and tested separately on data produced by one speaker. The reported results show even for PhonDat a difference in performance between speakers. Another aspect that can have a great impact on the model result is the quality of the input data. While PhonDat was manually segmented and annotated, Verbmobil was processed automatically using the MAUS segmentation system. When evaluating outliers we found many examples of wrong segmentation, as we also discussed in Section 4.2.

@@

\begin{table}[htbp]
\centering
%\vspace{10mm}
\begin{tabular}{|l|c|c|c|c|}

\hline
	 & \shortstack{Train: whole \\ Test: unseen speaker} & \shortstack{Train\&Test (+SR): \\ speaker AKX} & \shortstack{Train\&Test (-SR): \\ speaker AKX} \\ 
\hline
\hline
Correlation coef 		& .76   & .75 & .63 \\
	\hline
MAE  &  22.91 & 22.47 & 26.95 \\
	\hline
RMSE  &  40.36 & 33.87 & 40.30 \\
	\hline

\end{tabular}
\caption{} 
\label{tab:perfM}
\end{table}
